
cumentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.5in, bottom=0.4in, left=0.55in, right=0.55in]{geometry}
\usepackage{graphicx}
 
\usepackage{multicol}
\usepackage{url}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}
\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=10.3in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-1.1pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{1\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}}
%-----------------------------------------------------------

\begin{document}
\hspace{0.5cm}\\[-0.2cm]
\textbf{\Huge{\Huge{Shivank Garg}}}\\ 
 Second year Undergraduate \hfill \textbf{shivankg@iitk.ac.in} \\
 Department of Electrical Engineering \hfill (+91)-9680\,469\,015\\
\resheading{\textbf{EDUCATIONAL QUALIFICATIONS}}\\[\lsep]
\vspace{.23cm}
\begin{center}
\indent \begin{tabular}{ | @{\hspace{1.7em}}l@{\hspace{1.7em}} | @{\hspace{1.7em}}c @{\hspace{1.7em}}| @{\hspace{1.7em}}c@{\hspace{1.7em}} | @{\hspace{1.7em}}c@{\hspace{1.7em}} | }
\hline
\textbf{Year} & \textbf{Degree} & \textbf{Institute} & \textbf{CPI / \%} \\
\hline \hline 
2020* & {B.Tech. in Electrical Engineering} & Indian Institute of Technology, Kanpur & 7.9/10\\
2016 & Class XII, CBSE & Emmanuel Mission School & 93.6\% \\
2014 & Class X, CBSE & St. Francis School & 10/10 \\
\hline
\end{tabular}
\end{center}
\resheading{\textbf{ACADEMIC ACHIEVEMENTS}}\\[\lsep] \vspace{.1cm}
\begin{itemize}
\item \noindent Secured \textbf{All India Rank 729} in Joint Entrance Examination(JEE Advanced) 2016 among 200,000 students \vspace{-.55em}
\item \noindent Secured \textbf{All India Rank 2190} in Joint Entrance Examination(JEE MAINS) 2016 among 1,600,000 students

\end{itemize}
\resheading{\textbf{TECHNICAL SKILLS} }\vspace{1.8em}\\[\lsep]
\textbf{Languages - } C, C++, Python, HTML, CSS. \hspace{4cm} \textbf{Operating Systems} - Windows, Linux Systems. \\
\textbf{Software and Tools - }  MATLAB, Fusion360, \LaTeX, Git, MS Office. \hspace{.45cm} \textbf{Web Development - } HTML, CSS, Google mdl\\
\textbf{Hardware - } Arduino, Various sensors and Communication Modules.\vspace{.2cm}\\ 
\resheading{\textbf{TECHNICAL PROJECTS}}\\[\lsep] \vspace{.2cm}
\begin{itemize}
\item \textbf{Prosthetic Arm} \hfill \textit{May'17 - July'17} \\
 \emph{Robotics Club, Science and Technology Council, IITK} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Project aimed at designing and controlling an artificial gripper (3-D printed) based on concept of prosthesis.
	\item Designed the hand on Fusion360 and controlled it using Servos and Strings like tendons do in humans.
	\item Implemented flex sensors and Bluetooth modules for sending signals to 3D printed gripper.
	\item This Project represented IITK in \textbf{Inter-IIT Tech Meet 2018} in Engineer's Conclave.
	\item Awarded with \textbf{Best Social Project}, 2017 amongst the various summer projects. 
	\end{itemize}

\item \textbf{Automatic Crossbow} \hfill \textit{Aug'17 - Nov'17} \\
 \emph{Mentored by Prof. Shobhit Omar} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item A Technical Art project aimed at designing and fabricating a crossbow which shoots arrows automatically.
	\item Manufactured it using metallurgical processes and led the team of five.
	\item Uses the rotary motion to shoot the arrows, and reloading is similar to that of earlier machine guns.
	\end{itemize}
\end{itemize}
\\
\resheading{\textbf{RELEVANT COURSES} }\\[\lsep] \\ \\
\begin{center} \\[-0.5cm]
\begin{tabular}{|c|c|c|}
    \hline \vspace{.05cm}
     EE200-Signals, Systems and Networks  & PHY103-Electrodynamics & ESC101-Introduction to Computing \\ \vspace{.05cm}
     MTH102A-Linear Algebra and ODE & ESC201-Introduction to Electronics & MSO201A* - Probability and Statistics \\ \vspace{.05cm}
     EE250A* - Control System Analysis & EE210A*-Micro-Electronics-1 & ESO207-Data Structures and Algorithms \\ \hline
\end{tabular}
\end{center}
\flushright{* represents ongoing courses}\\
\resheading{\textbf{POSITIONS OF RESPONSIBILITY} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Secretary, Robotics Club, IIT Kanpur} \hfill \textit{Apr'17 - Current}\\ \vspace{-.1cm}
    \begin{itemize}\itemsep \isep
        \item Promoted Robotics as a hobby in IITK community through variety of workshops, competitions, hackathons.
        \item Mentored and assisted many first year students to start their journey as a robotics enthusiast.
    \end{itemize}\\ \vspace{-.1cm}
\item \noindent \textbf{Election Officer, General Election’17}\\ \vspace{-.2cm}
    \begin{itemize} \itemsep \isep
        \item Worked in three tier team for successful conduction of free and fair elections in IITK community.
    \end{itemize}
\end{itemize}
\resheading{\textbf{SOCIAL INITIATIVES}}\\[\lsep]
\begin{itemize}
\item \textbf{PRAYAS} \hfill \textit{Dec'16 - Aug'17} \\
 \emph{An IIT Kanpur initiative} \\ \vspace{-0.1cm}
    \begin{itemize}\itemsep \isep
        \item Aimed to make quality education accessible to those who are deprived of it.
        \item To inculcate values and provide moral education to the students.
    \end{itemize}
\item \textbf{Member of National Cadet Corps(NCC)} \hfill \textit{Aug'16 - Apr'17} \\
 \emph{2 UP CTR}\\ \vspace{-0.1cm}
    \begin{itemize}
        \item Aimed at creating a human resource of Organized, Trained and Motivated youth.
        \item To Develop Character, Comradeship, Discipline, Leadership, Secular Outlook, Spirit of Adventure, and Ideals of Selfless Service amongst the Youth of the Country.
    \end{itemize}
\end{itemize}
\end{document}


